Review of Assigned Readings

### 2017-12-26 documentation/documentation.tex
add functionality for first difference and log first difference (nr of tweets, btc close price)
adding @online bibliography and text about tweepy

\section{Data Collection}
Here, we provide a detailed description of how the data for the sequential analysis is gathered and stored. This includes two  subsections the (1) tweets data and the (2) bitcoin price data.
\subsection{Tweets Data}
To collect the needed twitter data a python script has been written and the real-time twitter data were streamed and stored by the usage of a raspberry pi.
\subsubsection{Python Script}
Twitter offers different Application Programming Interfaces (API) for collecting data. Based on twitter, the four most relevant API's are (1) Ads API, (2) Filter realtime Tweets, (3) Search Tweets and (3)Direct Message API. However, the timeframe for gathering data for free is limited to 7 day's.
....
....

>>>>

\section{Data Collection}
Here, we provide a detailed description of how the data for the sequential analysis is gathered and stored. This includes two  subsections the (1) tweets data and the (2) bitcoin price data.
\subsection{Tweets Data}
To collect the needed twitter data a python script has been written. Whit the python script real-time twitter data are streamed and stored by the usage of a raspberry pi.
\subsubsection{Python Script}
Twitter offers different Application Programming Interfaces (API) for collecting data. Based on twitter, the biggest an probably most relevant API's are (1) Ads API, (2) Filter realtime Tweets, (3) Search Tweets and (3)Direct Message API. (How to add a reference???) However, the timeframe for gathering data for free is limited to 7 day's. As python offers different libaries tweepy a open-source libary is been used for streaming the data. By using tweepy twitter can be reached in two way's (??) or by the streaming API. The latter has been used in contex of the assignment.

Stream - push then pull, easier
- authentic
\subsubsubsection{Twitter Authentification}
- printscreens and how to proceed
- pip install??

\subsubsubsection{Twitter Streaming API}
....
....
